Using temperature distributions of active regions to investigate flare activity

### 2014-12-16 paper.tex
More description of temperature map method added

@@

%===========================================================================
\section{Method}
\subsection{Temperature analysis}
The core of this analysis is the temperature map method described by \cite{Leonard2014} (henceforth Paper I).
Briefly, this method compares the relative brightnesses in each AIA wavelength channel at a given time and infers the best-fitting temperature from that comparison.
This allows the temperature of the corona to be estimated for every pixel of an AIA image, resulting in very high resolution temperature maps.

\subsection{Active region analysis}
The method of Paper I was used to investigate the temperatures of the active regions associated with flares which occured betwen 2011-02-01 and 2011-04-01.
% Currently the dates are 2011/02/10 - 2011/02/16, which needs some fixing
The first part of the investigation tracked active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
Then the temperatures of the associated active regions were directly compared for each of the investigated flares.

@@

%===========================================================================
\section{Discussion and conclusions}

>>>>

Although it is faster than others of its kind, the temperature-calculating method used here takes some time to analyse all the required data.
As such this is a preliminary work and the results should not be considered definitive.
Rather they are a demonstration of the type of study made available by fast temperature analysis of the corona, which until recently has not been possible.

@@

%===========================================================================
\section{Method}
\subsection{Temperature analysis}
The core of this analysis is the temperature map method described by \cite{Leonard2014} (henceforth Paper I).
Briefly, this method compares the relative brightnesses in each AIA wavelength channel at a given time and infers the best-fitting temperature from that comparison.
This allows the temperature of the corona to be estimated for every pixel of an AIA image, resulting in very high resolution temperature maps.
Crucially, this method produces temperature maps extremely quickly, which allows us to investigate coronal temperatures during localised dynamic events such as flares.
With other, slower methods, such studies are infeasible due to the computation time required.
An example temperature map is shown in Figure X. % Include an example temperature map

\subsection{Active region analysis}
The method of Paper I was used to investigate the temperatures of the active regions associated with flares which occured betwen 2011-02-01 and 2011-04-01.
The specific active regions investigated are listed in Table X along with the flares associated with each. % Include a table of the flares looked at, when they occured and which active region they're associated with.
The first part of the investigation tracked the active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
Then the temperatures of the associated active regions were directly compared for each of the investigated flares.

@@

%===========================================================================
\section{Discussion and conclusions}
From this study, it appears that there is no clear link between solar flares and coronal temperatures.
However, it is worth remembering that
